Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-09-18 main.tex
some updates

When $\calT$ is a triangulation and $T \in \calT$, then $\patch_{\calT}(T)$ denotes the \emph{local patch} or \textit{local star} of $T$, 
which is the simplicial subcomplex of $\calT$ that contains all supersimplices of $T$ and their subsimplices. 
We write $\carapace_{\calT}(T)$ for the subset of the local patch whose members do not contain $T$ itself. 
Formally,
\begin{gather*}
    % \patch_{\calT}(T) := \bigcup_{ T' \in \supsimplex(\calT,T) } \subsimplex(T'),
    \patch_{\calT}(T) := \bigcup_{ \substack{ T' \in \subsimplex_{n}(\calT) \\ T \subseteq T' } } \subsimplex(T'),
    \qquad 
    \carapace_{\calT}(T) := \bigcup_{ \substack{ T' \in \patch_{\calT}(T) \\ T \nsubseteq T' } } \subsimplex(T').
\end{gather*}
We also write $U_T := | \patch_{\calT}(T) |$ for the underlying set of the local patch. 
A crucial structural observation is the following.~\footnote{$U_T$ looks open but it is not. With closed simplices, the patches are disjoint if they essentially disjoint.}

@@

Whenever $\calT$ is a strongly connected $n$-dimensional triangulation, 
a \emph{spanning tree} is an enumeration of the all $n$-dimensional simplices $T_{0}, \dots, T_{M}$
where for each $1 \leq m \leq M$ we have fixed $0 \leq j(m) \leq m-1$ such that 
$T_{m}$ and $T_{j(m)}$ share a common face of dimension $n-1$.
We call $T_{j(m)}$ the \emph{predecessor} of $T_{m}$ within the spanning tree.

@@

\begin{theorem}\label{theorem:poincarefriedrichsestimate:grad}
    Let $\Omega \subseteq \bbR^{n}$ be a domain with a strongly-connected finite triangulation $\calT$.
    Let $T_0 \in \calT$ be an $n$-simplex such that for all $n$-simplices $T \in \calT$ 
    we fix a strong path $T_0, T_1, \dots, T_m = T$.
    Suppose $1 \leq p,q \leq \infty$ with $1 = 1/p + 1/q$.
    Then for any $u \in W^{1,p}(\Omega)$ 
    there exists $w \in W^{1,p}(\Omega)$ with $\nabla u = \nabla w$ 
    and such that for all $T \in \calT$:
%     DONE {Make sure the notation for the PF constants is uniform throughout the paper}
    \begin{align*} 
        % \color{red}
        \| w \|_{L^{p}(T_m)}
        &\leq 
        \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{\frac 1 q}
        \sum_{t=1}^{m}
        \volumeratio(\calT)^{\frac{m-t}{p}}
        C_{{\rm{PF}},T_{t} \cup T_{t-1},p}
        % 2 C_{\PF,{\rm EFNT},p} \volumeratio(\calT)^{\frac 1 p} \max\left( \diam(T_{t}), \diam(T_{t-1}) \right)
        \| \nabla u \|_{L^{p}(T_{t} \cup T_{t-1})}
        \\&\quad \quad \quad 
        +
        \volumeratio(\calT)^{\frac{m-1}{p}}
        % C_{\PF,{\rm EFNT},p} \diam(T_0)
        C_{{\rm{PF}},T_{0},p}
        \| \nabla u \|_{L^{p}(T_{0})}
        .
    \end{align*}
\end{theorem}

@@

 We construct the potential recursively. 
 We have seen that $c_{0} = w_{0} - u_{|\Omega_{0}}$ is a constant. 
 Assume that $1 \leq m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ 
 such that $c_{0} = w_{m-1} - u_{|\Omega_{m-1}}$ is the constant above. 
 % Note that this assumption is already satisfied when $m=1$.
 Hence $\nabla w_{m-1} = \nabla u$ over $\Omega_{m-1}$. 
 By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{{m-1}}$. 
 Since $$\nabla w_{F_{m}|T_{{m-1}}} = \nabla w_{m-1|T_{{m-1}}},$$
 there exists a constant $$c_{m} := w_{m-1|T_{{m-1}}} - w_{F_{m}|T_{{m-1}}}.$$
 We define $w'_{F_m} := w_{F_m} + c_{m} \in W^{1,p}(U_F)$.
 By construction, $$\nabla w'_{F_m} = \nabla w_{F_m} = \nabla u_{|U_{F_m}}$$ 
 and 
 $w'_{F_{m}|T_{{m-1}}} = w_{m-1|T_{{m-1}}}$. 
 But that already implies $w'_{F_m} = w_{|F_m} - c_{0}$. 
 Letting $w_{m} \in W^{1,p}(\Omega_m)$ by extending $w_{m-1}$ with $w'_{F_m|T_m}$,
 we have $c_{0} = w_{m} - u_{|\Omega_{m}}$.

 We assess the norm of this potential. We observe 
 \begin{gather*}
    \| w'_{F_m} \|_{L^{p}(T_m)}
    \leq 
    \| w_{F_m} \|_{L^{p}(T_m)}
    +
    \| c_{m} \|_{L^{p}(T_m)},
    \\
    \| c_{m} \|_{L^{p}(T_m)}
    = 
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
    \| c_{m} \|_{L^{p}(T_{{m-1}})},
    \\ 
    \| c_{m} \|_{L^{p}(T_{{m-1}})}
    \leq 
    \| w_{m-1}\|_{L^{p}(T_{{m-1}})} + \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})} 
    .
 \end{gather*}
 In particular,
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}
    &
    \leq 
    \| w_{F_m} \|_{L^{p}(T_m)}
    \\&\qquad 
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
    \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})}
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
    \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
    .
 \end{align*}
 We sum the two integrals of $w_{F_m}$. 
 % 
 In the special case $p=1$,
 \begin{align*}
    \| w_{m} \|_{L^{1}(T_m)}
    \leq 
    \max\left(
        1, \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) } 
    \right)
    \| w_{F_m} \|_{L^{1}(U_{F_m})}
    +
    \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) }
    \| w_{m-1}\|_{L^{1}(T_{{m-1}})}
    .
 \end{align*}
 In the special case $p=\infty$, 
 \begin{align*}
    \| w_{m} \|_{L^{\infty}(T_m)}
    \leq 
    2
    \| w_{F_m} \|_{L^{\infty}(U_{F_m})}
    +
    \| w_{m-1}\|_{L^{\infty}(T_{{m-1}})}
    .
 \end{align*}
 % 1/q = 1 - 1/p = (p-1)/p 
 When $1 < p < \infty$, letting $q := p/(p-1) \in (1,\infty)$ be the complementary exponent, we observe 
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}
    &\leq 
    \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
    \left( 
        \| w_{F_{m}} \|_{L^{p}(T_m)}^{p}
        +
        \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})}^{p}
    \right)^{\frac 1 p}
    \\&\qquad 
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
    \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
    \\&\leq 
    \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
    \| w_{F_{m}} \|_{L^{p}(U_{F_m})} 
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
    \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
    .
 \end{align*}
 Recursive application provides the following estimate:
%  if $T_0 = S_0, S_1, \dots, S_m = T_m$ is a sequence of $n$-simplices in $\calT$
%  such that \color{red}$S_{t-1}$ precedes $S_{t}$ in the graph \color{black} and such that $F_t = S_t \cap S_{t-1}$,
%  then 
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}
    &\leq 
    \sum_{t=1}^{m} 
    \left( 
        \prod_{t < l \leq m} 
        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{l-1})^{\frac 1 p} } 
    \right)
    \left( 1 + \frac{ \vol(T_t)^{\frac q p} }{ \vol(T_{t-1})^{\frac q p} } \right)^{\frac 1 q}
    \| w_{F_t} \|_{L^{p}(U_{F_t})}
    \\&\quad \quad \quad 
    +
    \left( 
        \prod_{0 < l \leq m} 
        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{l-1})^{\frac 1 p} } 
    \right)
    \| w_{T_0}\|_{L^{p}(T_{0})}
    .
 \end{align*}
 % Taking into account Definition~\eqref{math:todo}, we obtain the desired inequality. % TODO: what was originally used here?
 We obtain the desired estimate. 
%  \begin{align*}
%     \| w_{m} \|_{L^{p}(T_m)}^{p}
%     &\leq 
%     (m+1)^{p-1}
%     % \sum_{t=1}^{m} \volumeratio(\calT)^{m-t} 
%     % \sum_{t=0}^{m-1} \volumeratio(\calT)^{t} 
%     \frac{\volumeratio(\calT)^{m}-1}{\volumeratio(\calT)-1}
%     \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{p/q}
%     \| w_{F_t} \|_{L^{p}(U_{F_t})}^{p}
%     \\&\quad \quad \quad 
%     +
%     (m+1)^{p-1}
%     \volumeratio(\calT)^{m-1}
%     \| w_{T_0}\|_{L^{p}(T_{0})}^{p}
%     .
%  \end{align*}
%  Notice that $p/q = p - 1$.
 % 
 Repeating this argument produces $w \in L^{p}(\Omega)$ 
 such that for all $n$-simplices $T \in \calT$ we have the restriction $w_{|T} \in W^{1,p}(T)$ with $w_{|T} = u + c_{0}$.
 In particular, $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$.
\end{proof}

@@

We refer the reader to Ern and Guermond~\cite{ern2021finite} and Hiptmair~\cite{hiptmair2002finite} for further background material on Sobolev vector analysis. 
Exterior algebra and exterior products are reviewed in the textbooks by Greub~\cite{greub1967multilinear} and Lee~\cite{lee2012smooth}.

We discuss the Sobolev spaces of vector calculus and their transformation behavior. 
Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
First, recall that $L^{p}(\Omega)$ is the space of scalar-valued $p$-integrable functions defined on $\Omega$
and that $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for vector-valued functions with each component in $L^{p}(\Omega)$. 
In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
$W^{p}(\grad,\Omega) := W^{1,p}(\Omega)$ is the space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$, that is,  
\begin{gather*}
    W^{p}(\grad,\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
    .
\end{gather*}
The space $\bfW^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are defined as 
\begin{gather*}
    \bfW^{p}(\curl,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \curl \bfu \in \bfL^{p}(\Omega) \},
    \\ 
    \bfW^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
\end{gather*}
We are interested in transformations of these Sobolev tensor fields from one domain onto another. 
Suppose that $\Omega, \Omega' \subset \mathbb{R}^3$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
The gradient-, curl-, divergence-conforming Piola transformations are the mappings 
$\phi^{\grad}: L^{p}(\Omega') \to L^{p}(\Omega)$,
$\phi^{\curl}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$, 
$\phi^{\divergence}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$,
and
$\phi^{\rm b}: L^{p}(\Omega') \to L^{p}(\Omega)$. 
We define them 
for any $v \in L^{p}(\Omega')$ and $\bfw \in \bfL^{p}(\Omega')$ by setting 
\begin{subequations}\label{eq_definition_piola}
\begin{align*}
    \phi^{\grad}(v) &= v \circ \phi, \\
    \phi^{\curl}(\bfw) &= \Jacobian\phi^{T} (\bfw \circ \phi), \\
    \phi^{\divergence}(\bfw) &= \adj(\Jacobian\phi) \left( \bfw \circ \phi \right), \\  
    \phi^{\rm b}(v) &= \det(\Jacobian\phi) \left( v \circ \phi \right),
\end{align*}
\end{subequations}
and where $\Jacobian\phi$ is the Jacobian matrix of $\phi$; see also~\cite[Definition~9.8]{ern2021finite}.
These mappings are invertible. 
Bounds on the Lebesgue norms will follow from a more general result below.

We use the commutativity relations 
\begin{subequations}\label{eq_piola_commute}
\begin{align}
    \grad \phi^{\grad} (v) &= \phi^{\curl}(\grad v), 
    \\
    \curl \phi^{\curl}(\bfv) &= \phi^{\divergence}(\curl \bfv), 
    \\
    \divergence \phi^{\divergence}(\bfw) &= \phi^{\rm b}(\divergence \bfw),
\end{align}
\end{subequations}
where $v \in W^{p}(\grad,\Omega)$, $\bfv \in \bfW^{p}(\curl,\Omega)$, and $\bfw \in \bfW^{p}(\divergence,\Omega)$.  
We summarize this as a commuting diagram:
\begin{align*}
    \begin{CD}
        W^{p}(\grad,\Omega') @>{\grad}>> \bfW^{p}(\curl,\Omega') @>{\curl}>> \bfW^{p}(\divergence,\Omega') @>{\divergence}>> L^{p}(\Omega')
        \\
        @VV{\phi^{\grad}}V 
        @VV{\phi^{\curl}}V 
        @VV{\phi^{\divergence}}V 
        @VV{\phi^{\rm b}}V 
        \\
        W^{p}(\grad,\Omega ) @>{\grad}>> \bfW^{p}(\curl,\Omega ) @>{\curl}>> \bfW^{p}(\divergence,\Omega ) @>{\divergence}>> L^{p}(\Omega ).
    \end{CD}
\end{align*}

\begin{remark}
    The Piola transform goes into the opposite direction of the mapping $\phi : \Omega \rightarrow \Omega'$:
    % Our notion of Piola transform along a mapping $\phi : \Omega \rightarrow \Omega'$ goes in the opposite direction of the mapping:
    scalar and vector fields over $\Omega'$ are transformed into scalar and vector fields over $\Omega$.
    This definition is in accordance with the notion of pullback, which we will review shortly. 
    One advantage of that definition is that it also makes sense whenever the transformation is not a diffeomorphism. 
    The literature also knows the Piola transform in the direction of the original mapping. 
\end{remark}

>>>>

When $\calT$ is a triangulation and $T \in \calT$, then $\patch_{\calT}(T)$ denotes the \emph{local patch} or \textit{local star} of $T$, 
which is the simplicial subcomplex of $\calT$ that contains all supersimplices of $T$ and their subsimplices. 
We write $\carapace_{\calT}(T)$ for the subset of the local patch whose members do not contain $T$ itself. 
Formally,
\begin{gather*}
    % \patch_{\calT}(T) := \bigcup_{ T' \in \supsimplex(\calT,T) } \subsimplex(T'),
    \patch_{\calT}(T) := \bigcup_{ \substack{ T' \in \subsimplex_{n}(\calT) \\ T \subseteq T' } } \subsimplex(T'),
    \qquad 
    \carapace_{\calT}(T) := \bigcup_{ \substack{ T' \in \patch_{\calT}(T) \\ T \nsubseteq T' } } \subsimplex(T').
\end{gather*}
We also write $U_T := | \patch_{\calT}(T) |$ for the underlying set of the local patch. 
A crucial structural observation is the following.~\footnote{\todo{$U_T$ looks open but it is not. With closed simplices, the patches are disjoint if they essentially disjoint.}}

@@

@@

\begin{theorem}\label{theorem:poincarefriedrichsestimate:grad}
    Let $\Omega \subseteq \bbR^{n}$ be a domain with a strongly-connected finite triangulation $\calT$.
    Let $T_0 \in \calT$ be an $n$-simplex such that for all $n$-simplices $T \in \calT$ 
    we fix a strong path $T_0, T_1, \dots, T_m = T$.
    Suppose $1 \leq p,q \leq \infty$ with $1 = 1/p + 1/q$.
    Then for any $u \in W^{1,p}(\Omega)$ 
    there exists $w \in W^{1,p}(\Omega)$ with $\nabla u = \nabla w$ 
    and such that for all $T \in \calT$:
%     DONE {Make sure the notation for the PF constants is uniform throughout the paper}
    \begin{align*} 
        % \color{red}
        \| w \|_{L^{p}(T_m)}
        &\leq 
        \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{\frac 1 q}
        \sum_{t=1}^{m}
        \volumeratio(\calT)^{\frac{m-t}{p}}
        C_{{\rm{PF}},T_{t} \cup T_{t-1},p}
        % 2 C_{\PF,{\rm EFNT},p} \volumeratio(\calT)^{\frac 1 p} \max\left( \diam(T_{t}), \diam(T_{t-1}) \right)
        \| \nabla u \|_{L^{p}(T_{t} \cup T_{t-1})}
        \\&\quad \quad \quad 
        +
        \volumeratio(\calT)^{\frac{m-1}{p}}
        % C_{\PF,{\rm EFNT},p} \diam(T_0)
        C_{{\rm{PF}},T_{0},p}
        \| \nabla u \|_{L^{p}(T_{0})}
        .
    \end{align*}
    \todo{Rewrite this result.}
    When $1 < p < \infty$, letting $q := p/(p-1) \in (1,\infty)$ be the complementary exponent, we observe 
    \begin{align*}
        \| w_{m} \|_{L^{p}(T_m)}
        &\leq 
        \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
        \left( 
            \| w_{F_{m}} \|_{L^{p}(T_m)}^{p}
            +
            \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})}^{p}
        \right)^{\frac 1 p}
        \\&\qquad 
        +
        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
        \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
        \\&\leq 
        \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
        \| w_{F_{m}} \|_{L^{p}(U_{F_m})} 
        +
        \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
        \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
        .
    \end{align*}
\end{theorem}

@@

 We construct the potential recursively. 
 We have seen that $c_{0} = w_{0} - u_{|\Omega_{0}}$ is a constant. 
 Assume that $1 \leq m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ 
 such that $c_{0} = w_{m-1} - u_{|\Omega_{m-1}}$ is the constant above. 
 % Note that this assumption is already satisfied when $m=1$.
 Hence $\nabla w_{m-1} = \nabla u$ over $\Omega_{m-1}$. 
 By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{{m-1}}$. 
 Since $$\nabla w_{F_{m}|T_{{m-1}}} = \nabla w_{m-1|T_{{m-1}}},$$
 there exists a constant $$c_{m} := w_{m-1|T_{{m-1}}} - w_{F_{m}|T_{{m-1}}}.$$
 We define $w'_{F_m} := w_{F_m} + c_{m} \in W^{1,p}(U_F)$.
 By construction, $$\nabla w'_{F_m} = \nabla w_{F_m} = \nabla u_{|U_{F_m}}$$ 
 and 
 $w'_{F_{m}|T_{{m-1}}} = w_{m-1|T_{{m-1}}}$. 
 But that already implies $w'_{F_m} = w_{|F_m} - c_{0}$. 
 Defining $w_{m} \in W^{1,p}(\Omega_m)$ by extending $w_{m-1}$ with $w'_{F_m|T_m}$,
 we have $c_{0} = w_{m} - u_{|\Omega_{m}}$.

 We assess the norm of this potential. We observe 
 \begin{gather*}
    \| w_{m} \|_{L^{p}(T_m)}
    =
    \| w'_{F_m} \|_{L^{p}(T_m)}
    \leq 
    \| w_{F_m} \|_{L^{p}(T_m)}
    +
    \| c_{m} \|_{L^{p}(T_m)},
    \\
    \| c_{m} \|_{L^{p}(T_m)}
    = 
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
    \| c_{m} \|_{L^{p}(T_{{m-1}})},
    \\ 
    \| c_{m} \|_{L^{p}(T_{{m-1}})}
    \leq 
    \| w_{m-1}\|_{L^{p}(T_{{m-1}})} + \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})} 
    .
 \end{gather*}
 In particular,
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}
    &
    \leq 
    \| w_{F_m} \|_{L^{p}(T_m)}
    \\&\qquad 
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
    \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})}
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
    \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
    .
 \end{align*}
 We sum the two integrals of $w_{F_m}$. 
 % 
 In the special case $p=1$,
 \begin{align*}
    \| w_{m} \|_{L^{1}(T_m)}
    \leq 
    \max\left(
        1, \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) } 
    \right)
    \| w_{F_m} \|_{L^{1}(U_{F_m})}
    +
    \frac{ \vol(T_m) }{ \vol(T_{{m-1}}) }
    \| w_{m-1}\|_{L^{1}(T_{{m-1}})}
    .
 \end{align*}
 In the special case $p=\infty$, 
 \begin{align*}
    \| w_{m} \|_{L^{\infty}(T_m)}
    \leq 
    2
    \| w_{F_m} \|_{L^{\infty}(U_{F_m})}
    +
    \| w_{m-1}\|_{L^{\infty}(T_{{m-1}})}
    .
 \end{align*}
 % 1/q = 1 - 1/p = (p-1)/p 
 When $1 < p < \infty$, letting $q := p/(p-1) \in (1,\infty)$ be the complementary exponent, we observe 
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}
    &\leq 
    \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
    \left( 
        \| w_{F_{m}} \|_{L^{p}(T_m)}^{p}
        +
        \| w_{F_{m}} \|_{L^{p}(T_{{m-1}})}^{p}
    \right)^{\frac 1 p}
    \\&\qquad 
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
    \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
    \\&\leq 
    \left( 1 + \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{{m-1}})^{\frac q p} } \right)^{\frac 1 q}
    \| w_{F_{m}} \|_{L^{p}(U_{F_m})} 
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{{m-1}})^{\frac 1 p} }
    \| w_{m-1}\|_{L^{p}(T_{{m-1}})}
    .
 \end{align*}
 Recursive application provides the following estimate:
%  if $T_0 = S_0, S_1, \dots, S_m = T_m$ is a sequence of $n$-simplices in $\calT$
%  such that \color{red}$S_{t-1}$ precedes $S_{t}$ in the graph \color{black} and such that $F_t = S_t \cap S_{t-1}$,
%  then 
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}
    &\leq 
    \sum_{t=1}^{m} 
    \left( 
        \prod_{t < l \leq m} 
        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{l-1})^{\frac 1 p} } 
    \right)
    \left( 1 + \frac{ \vol(T_t)^{\frac q p} }{ \vol(T_{t-1})^{\frac q p} } \right)^{\frac 1 q}
    \| w_{F_t} \|_{L^{p}(U_{F_t})}
    \\&\quad \quad \quad 
    +
    \left( 
        \prod_{0 < l \leq m} 
        \frac{ \vol(T_l)^{\frac 1 p} }{ \vol(T_{l-1})^{\frac 1 p} } 
    \right)
    \| w_{T_0}\|_{L^{p}(T_{0})}
    .
 \end{align*}
 % Taking into account Definition~\eqref{math:todo}, we obtain the desired inequality. % TODO: what was originally used here?
 We obtain the desired estimate. 
%  \begin{align*}
%     \| w_{m} \|_{L^{p}(T_m)}^{p}
%     &\leq 
%     (m+1)^{p-1}
%     % \sum_{t=1}^{m} \volumeratio(\calT)^{m-t} 
%     % \sum_{t=0}^{m-1} \volumeratio(\calT)^{t} 
%     \frac{\volumeratio(\calT)^{m}-1}{\volumeratio(\calT)-1}
%     \left( 1 + \volumeratio(\calT)^{\frac q p} \right)^{p/q}
%     \| w_{F_t} \|_{L^{p}(U_{F_t})}^{p}
%     \\&\quad \quad \quad 
%     +
%     (m+1)^{p-1}
%     \volumeratio(\calT)^{m-1}
%     \| w_{T_0}\|_{L^{p}(T_{0})}^{p}
%     .
%  \end{align*}
%  Notice that $p/q = p - 1$.
 % 
 Repeating this argument produces $w \in L^{p}(\Omega)$ 
 such that for all $n$-simplices $T \in \calT$ we have the restriction $w_{|T} \in W^{1,p}(T)$ with $w_{|T} = u + c_{0}$.
 In particular, $w \in W^{1,p}(\Omega)$ with $\nabla w = \nabla u$.
\end{proof}

@@

We discuss the Sobolev spaces of vector calculus and exterior calculus 
with particular emphasis on their transformation behavior. 
We refer the reader to Ern and Guermond~\cite{ern2021finite} and Hiptmair~\cite{hiptmair2002finite} for further background material on Sobolev vector analysis. 
Exterior algebra and exterior products are reviewed in the textbooks by Greub~\cite{greub1967multilinear} and Lee~\cite{lee2012smooth}.

Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
First, recall that $L^{p}(\Omega)$ is the space of scalar-valued $p$-integrable functions defined on $\Omega$
and that $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for vector-valued functions with each component in $L^{p}(\Omega)$. 
In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
% $W^{p}(\grad,\Omega) := W^{1,p}(\Omega)$ is 
The space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$ is 
\begin{gather*}
    W^{p}(\grad,\Omega) := W^{1,p}(\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
    .
\end{gather*}
The space $\bfW^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are written 
\begin{gather*}
    \bfW^{p}(\curl,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \curl \bfu \in \bfL^{p}(\Omega) \},
    \\ 
    \bfW^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
\end{gather*}
We are interested in transformations of these Sobolev tensor fields from one domain onto another. 
Suppose that $\Omega, \Omega' \subset \mathbb{R}^3$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
The gradient-, curl-, divergence-conforming Piola transformations are the mappings 
$\phi^{\grad}: L^{p}(\Omega') \to L^{p}(\Omega)$,
$\phi^{\curl}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$, 
$\phi^{\divergence}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$,
and
$\phi^{\rm b}: L^{p}(\Omega') \to L^{p}(\Omega)$. 
We define them 
for any $v \in L^{p}(\Omega')$ and $\bfw \in \bfL^{p}(\Omega')$ by setting 
\begin{subequations}\label{eq_definition_piola}
\begin{align*}
    \phi^{\grad}(v) &= v \circ \phi, \\
    \phi^{\curl}(\bfw) &= \Jacobian\phi^{T} (\bfw \circ \phi), \\
    \phi^{\divergence}(\bfw) &= \adj(\Jacobian\phi) \left( \bfw \circ \phi \right), \\  
    \phi^{\rm b}(v) &= \det(\Jacobian\phi) \left( v \circ \phi \right),
\end{align*}
\end{subequations}
and where $\Jacobian\phi$ is the Jacobian matrix of $\phi$; see also~\cite[Definition~9.8]{ern2021finite}.
These mappings are invertible. 
Bounds on the Lebesgue norms will follow from a more general result below. 
% 
We use the commutativity relations 
\begin{subequations}\label{eq_piola_commute}
\begin{align}
    \grad \phi^{\grad} (v) &= \phi^{\curl}(\grad v), 
    \\
    \curl \phi^{\curl}(\bfv) &= \phi^{\divergence}(\curl \bfv), 
    \\
    \divergence \phi^{\divergence}(\bfw) &= \phi^{\rm b}(\divergence \bfw),
\end{align}
\end{subequations}
where $v \in W^{p}(\grad,\Omega)$, $\bfv \in \bfW^{p}(\curl,\Omega)$, and $\bfw \in \bfW^{p}(\divergence,\Omega)$.  
We summarize this as a commuting diagram:
\begin{align*}
    \begin{CD}
        W^{p}(\grad,\Omega') @>{\grad}>> \bfW^{p}(\curl,\Omega') @>{\curl}>> \bfW^{p}(\divergence,\Omega') @>{\divergence}>> L^{p}(\Omega')
        \\
        @VV{\phi^{\grad}}V 
        @VV{\phi^{\curl}}V 
        @VV{\phi^{\divergence}}V 
        @VV{\phi^{\rm b}}V 
        \\
        W^{p}(\grad,\Omega ) @>{\grad}>> \bfW^{p}(\curl,\Omega ) @>{\curl}>> \bfW^{p}(\divergence,\Omega ) @>{\divergence}>> L^{p}(\Omega ).
    \end{CD}
\end{align*}

\begin{remark}
    The Piola transform goes into the opposite direction of the mapping $\phi : \Omega \rightarrow \Omega'$:
    % Our notion of Piola transform along a mapping $\phi : \Omega \rightarrow \Omega'$ goes in the opposite direction of the mapping:
    scalar and vector fields over $\Omega'$ are transformed into scalar and vector fields over $\Omega$.
    This definition is in accordance with the notion of pullback, which we will review shortly. 
    One advantage of that definition is that it also makes sense whenever the transformation is not onto. 
    In some literature conventions, the Piola transform is in the direction of the original mapping. 
\end{remark}
